---
title: "R Notebook"
output: html_notebook
author: Sushmita Maltare
---

This workflow is based on the article: TCGA Workflow: Analyze cancer genomics and epigenomics data using Bioconductor packages (Silva et al. 2016). Due to time and space limitations, we downloaded only a subset of the data, for a real analysis please use all data available. The data used in the examples are available in the package TCGAWorkflowData.

```{r}
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("TCGAWorkflowData")
```

Loading packages:
At the beginning of each section, the packages required to execute the code will be loaded. However, the following packages are required for all sections.

TCGAWorkflowData: this package contains the data necessary to execute each of the analysis steps. This is a subset of the downloaded to make the example faster. For a real analysis, please use all the data available.
DT: we will use it to visualize the results

```{r}
library(TCGAWorkflowData)
library(DT)
```


